The Privacy of Private Browsing

### 2013-12-15 finalproject/paper.tex
preparing to recompile pdf

    \subsection{Where To Look}
    Focused analysis of the hard drive can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from the hard drive's free space and slack space.\cite{ohana13} The 
    Windows pagefile (pagefile.sys on the hard drive) in particular can reveal
    private browsing artifacts. This file is where the least recently used 
    pages of memory are stored when too many applications are competing for the
    computer's physical memory. Browsing history and keywords used in internet 
    search engines have been discovered here.\cite{said11}

@@

    \subsection{Forensic Software}

>>>>

    \subsection{Where To Look}
    Focused analysis of the hard drive can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from the hard drive's free space and slack space.\cite{ohana13} The 
    Windows pagefile (pagefile.sys on the hard drive) in particular can reveal
    private browsing artifacts. This file is where the least recently used 
    pages of memory are stored when too many applications are competing for the
    computer's physical memory. Browsing history and keywords used in internet 
    search engines have been discovered here.\cite{said11} Free programs such 
	as \href{http://www.sleuthkit.org/autopsy/}{Autopsy} allow anyone to 
	investigate the free and slack space of a hard drive.

@@
